---
title: "ML performance"
author: "Jinglei Yu(s4830741)"
date: "2022/2/4"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Clear workspace:

```{r}
rm(list = ls())
```

load packages:
```{r}
library(plyr)
library(plotfunctions)
library(rsq)
```


load data for chained-regression:
```{r}
# all notes in original music 
end_Org <- 3824
pred_num <- 133

# predicted by all data
cr_all <- read.delim("predbychain_all.txt", sep = "", header = FALSE)
cr_prebyall <- cr_all[3825:3957,]

# predicted by train data
cr_sub <- read.delim("predbychain_test.txt", sep = "", header = FALSE)
cr_predbytrain <- cr_sub[3692:3824, ]

# last 133 notes in original music
original_end <- cr_all[3692:3824, ]
head(original_end)

```

load data for multistep:
```{r}
# predicted by all data 
## V0
m_all_0 <- read.delim("m_all_0.txt", sep = "", header = FALSE)
m_all_0[5] <- m_all_0[1] + m_all_0[2]*12

m_all_v0 <- as.data.frame(matrix(nrow=0,ncol=1))
rrange <- 1: nrow(m_all_0)

for (i in rrange){
rep <- as.data.frame(rep(m_all_0[i,5], m_all_0[i,4]))
m_all_v0 <- rbind(m_all_v0, rep)
}

## V1
m_all_1 <- read.delim("m_all_1.txt", sep = "", header = FALSE)
m_all_1[5] <- m_all_1[1] + m_all_1[2]*12

m_all_v1 <- as.data.frame(matrix(nrow=0,ncol=1))
rrange <- 1: nrow(m_all_1)

for (i in rrange){
rep <- as.data.frame(rep(m_all_0[i,5], m_all_1[i,4]))
m_all_v1 <- rbind(m_all_v1, rep)
}

## V2
m_all_2 <- read.delim("m_all_2.txt", sep = "", header = FALSE)
m_all_2[5] <- m_all_2[1] + m_all_2[2]*12

m_all_v2 <- as.data.frame(matrix(nrow=0,ncol=1))
rrange <- 1: nrow(m_all_2)

for (i in rrange){
rep <- as.data.frame(rep(m_all_2[i,5], m_all_2[i,4]))
m_all_v2 <- rbind(m_all_v2, rep)
}

## V3
m_all_3 <- read.delim("m_all_3.txt", sep = "", header = FALSE)
m_all_3[5] <- m_all_3[1] + m_all_3[2]*12

m_all_v3 <- as.data.frame(matrix(nrow=0,ncol=1))
rrange <- 1: nrow(m_all_3)

for (i in rrange){
rep <- as.data.frame(rep(m_all_3[i,5], m_all_3[i,4]))
m_all_v3 <- rbind(m_all_v3, rep)
}

## combine
m_all <- as.data.frame(cbind(m_all_v0[3825:3957,],
               m_all_v1[3825:3957,],
               m_all_v2[3825:3957,],
               m_all_v3[3825:3957,])) 


# predicted by train set
## V0
m_train_0 <- read.delim("m_pre_0.txt", sep = "", header = FALSE)
m_train_0[5] <- m_train_0[1] + m_train_0[2]*12

m_train_v0 <- as.data.frame(matrix(nrow=0,ncol=1))
rrange <- 1: nrow(m_train_0)

for (i in rrange){
rep <- as.data.frame(rep(m_train_0[i,5], m_train_0[i,4]))
m_train_v0 <- rbind(m_train_v0, rep)
}

## V1
m_train_1 <- read.delim("m_pre_1.txt", sep = "", header = FALSE)
m_train_1[5] <- m_train_1[1] + m_train_1[2]*12

m_train_v1 <- as.data.frame(matrix(nrow=0,ncol=1))
rrange <- 1: nrow(m_train_1)

for (i in rrange){
rep <- as.data.frame(rep(m_train_0[i,5], m_train_1[i,4]))
m_train_v1 <- rbind(m_train_v1, rep)
}

## V2
m_train_2 <- read.delim("m_pre_2.txt", sep = "", header = FALSE)
m_train_2[5] <- m_train_2[1] + m_train_2[2]*12

m_train_v2 <- as.data.frame(matrix(nrow=0,ncol=1))
rrange <- 1: nrow(m_train_2)

for (i in rrange){
rep <- as.data.frame(rep(m_train_2[i,5], m_train_2[i,4]))
m_train_v2 <- rbind(m_train_v2, rep)
}

## V3
m_train_3 <- read.delim("m_pre_3.txt", sep = "", header = FALSE)
m_train_3[5] <- m_train_3[1] + m_train_3[2]*12

m_train_v3 <- as.data.frame(matrix(nrow=0,ncol=1))
rrange <- 1: nrow(m_train_3)

for (i in rrange){
rep <- as.data.frame(rep(m_train_3[i,5], m_train_3[i,4]))
m_train_v3 <- rbind(m_train_v3, rep)
}

## combine
m_train <- as.data.frame(cbind(m_all_v0[3692:3824, ],
               m_all_v1[3692:3824, ],
               m_all_v2[3692:3824, ],
               m_all_v3[3692:3824, ])) 

head(m_train)
```

# Now we have:
original last 133 notes: original_end
predicted last 133 notes using cr: cr_predbytrain
predicted last 133 notes using multi: m_train

predicted next 133 notes using cr: cr_prebyall
predicted next 133 notes using multi: m_all

# Then do the comparasion:
As I've already done statistics calculation in Python before, I'll save the data and do it in python
```{r}
write.table (original_end, file ="original_end.csv", sep =",", row.names = FALSE)
write.table (cr_predbytrain, file ="cr_predbytrain.csv", sep =",", row.names = FALSE)
write.table (m_train, file ="m_train.csv", sep =",", row.names = FALSE)
write.table (cr_prebyall, file ="cr_prebyall.csv", sep =",", row.names = FALSE)
write.table (m_all, file ="m_all.csv", sep =",", row.names = FALSE)
```


## For train and test set:
Visualization:
For V1
```{r}
# Add extra space to right of plot area; change clipping to figure
par(mar=c(5.1, 4.1, 4.1, 15.1), xpd=TRUE)

## make a plot
plot(original_end$V1, ty="l", main = 'Prediction of the last 133 notes for voice 1',
     xlab = 'Note number', ylab = 'Note', 
     col = 'red')
lines(cr_predbytrain$V1, col = 'blue')
lines(m_train$V1, col = 'green')

legend('topright', inset=c(-0.75,0.2), cex = 0.8,
       legend=c('Original music', 'Prediciton by Chained-regression', 'Prediction by Step-wise classifier'),
       col=c('red', 'blue', 'green'), lty = 1,
       pch=c(NA, NA, NA), merge=TRUE)


```


```{r}
# Add extra space to right of plot area; change clipping to figure
par(mar=c(5.1, 4.1, 4.1, 15.1), xpd=TRUE)

## make a plot
plot(original_end$V2, ty="l", main = 'Prediction of the last 133 notes for voice 2',
     xlab = 'Note number', ylab = 'Note', 
     ylim = c(0,70),
     col = 'red')
lines(cr_predbytrain$V2, col = 'blue')
lines(m_train$V2, col = 'green')

legend('topright', inset=c(-0.75,0.2), cex = 0.8,
       legend=c('Original music', 'Prediciton by Chained-regression', 'Prediction by Step-wise classifier'),
       col=c('red', 'blue', 'green'), lty = 1,
       pch=c(NA, NA, NA), merge=TRUE)
```

```{r}
# Add extra space to right of plot area; change clipping to figure
par(mar=c(5.1, 4.1, 4.1, 15.1), xpd=TRUE)

## make a plot
plot(original_end$V3, ty="l", main = 'Prediction of the last 133 notes for voice 3',
     xlab = 'Note number', ylab = 'Note', 
     ylim = c(0,65),
     col = 'red')
lines(cr_predbytrain$V3, col = 'blue')
lines(m_train$V3, col = 'green')

legend('topright', inset=c(-0.75,0.2), cex = 0.8,
       legend=c('Original music', 'Prediciton by Chained-regression', 'Prediction by Step-wise classifier'),
       col=c('red', 'blue', 'green'), lty = 1,
       pch=c(NA, NA, NA), merge=TRUE)
```

```{r}
# Add extra space to right of plot area; change clipping to figure
par(mar=c(5.1, 4.1, 4.1, 15.1), xpd=TRUE)

## make a plot
plot(original_end$V4, ty="l", main = 'Prediction of the last 133 notes for voice 4',
     xlab = 'Note number', ylab = 'Note', 
     ylim = c(0,60),
     col = 'red')
lines(cr_predbytrain$V4, col = 'blue')
lines(m_train$V4, col = 'green')

legend('topright', inset=c(-0.75,0.2), cex = 0.8,
       legend=c('Original music', 'Prediciton by Chained-regression', 'Prediction by Step-wise classifier'),
       col=c('red', 'blue', 'green'), lty = 1,
       pch=c(NA, NA, NA), merge=TRUE)
```

## For all data

```{r}
# Add extra space to right of plot area; change clipping to figure
par(mar=c(5.1, 4.1, 4.1, 15.1), xpd=TRUE)

## make a plot
plot(cr_prebyall$V1, ty="l", main = 'Prediction of next 133 notes for voice 1',
     xlab = 'Note number', ylab = 'Note', 
     ylim = c(0,75),
     col = 'blue')
lines(m_all$V1, col = 'green')

legend('topright', inset=c(-0.75,0.2), cex = 0.8,
       legend=c('Prediciton by Chained-regression', 'Prediction by Step-wise classifier'),
       col=c('blue', 'green'), lty = 1,
       pch=c(NA, NA), merge=TRUE)
```

```{r}
# Add extra space to right of plot area; change clipping to figure
par(mar=c(5.1, 4.1, 4.1, 15.1), xpd=TRUE)

## make a plot
plot(cr_prebyall$V2, ty="l", main = 'Prediction of next 133 notes for voice 2',
     xlab = 'Note number', ylab = 'Note', 
     ylim = c(0,75),
     col = 'blue')
lines(m_all$V2, col = 'green')

legend('topright', inset=c(-0.75,0.2), cex = 0.8,
       legend=c('Prediciton by Chained-regression', 'Prediction by Step-wise classifier'),
       col=c('blue', 'green'), lty = 1,
       pch=c(NA, NA), merge=TRUE)
```


```{r}
# Add extra space to right of plot area; change clipping to figure
par(mar=c(5.1, 4.1, 4.1, 15.1), xpd=TRUE)

## make a plot
plot(cr_prebyall$V3, ty="l", main = 'Prediction of next 133 notes for voice 3',
     xlab = 'Note number', ylab = 'Note', 
     ylim = c(0,75),
     col = 'blue')
lines(m_all$V3, col = 'green')

legend('topright', inset=c(-0.75,0.2), cex = 0.8,
       legend=c('Prediciton by Chained-regression', 'Prediction by Step-wise classifier'),
       col=c('blue', 'green'), lty = 1,
       pch=c(NA, NA), merge=TRUE)
```


```{r}
# Add extra space to right of plot area; change clipping to figure
par(mar=c(5.1, 4.1, 4.1, 15.1), xpd=TRUE)

## make a plot
plot(cr_prebyall$V4, ty="l", main = 'Prediction of next 133 notes for voice 4',
     xlab = 'Note number', ylab = 'Note', 
     ylim = c(0,60),
     col = 'blue')
lines(m_all$V4, col = 'green')

legend('topright', inset=c(-0.75,0.2), cex = 0.8,
       legend=c('Prediciton by Chained-regression', 'Prediction by Step-wise classifier'),
       col=c('blue', 'green'), lty = 1,
       pch=c(NA, NA), merge=TRUE)
```



